---
title: "Simple Examples"
author: "Jason Orender"
date: "2022-12-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(largeLLE)
```

## Introduction

This is a set of simple examples meant to demonstrate basic usage as a
complement to the included vignettes.

### Binary Classification

This example fits binary classification data using a standard LASSO.  The colored
lines in the plot indicate the coefficient sizes at each lambda hyperparameter.

```{r}
 path <- system.file("data", package = "largeLLE")
 load(paste0(path,"/colon.RData"))
 message(sprintf("<< %d rows loaded, with %d features. >>", dim(colon$X)[1], dim(colon$X)[2]))
 
 llle_fit <- largeLLE(as.big.matrix(colon$X), as.matrix(colon$y), penalty = "lasso",
                      family = "binomial")
 
 plot(llle_fit)
```
Predicting new values of the respondent variable occurs in the standard way. Note
that a set of results for each lambda hyperparameter will be calculated (default
100 in most cases where the solution converges).

```{r}
pred <- predict(llle_fit, as.big.matrix(colon$X), type = "response")

best_lambda <- which.min(llle_fit$lambda)
results     <- pred[,best_lambda]
names(results) <- colon$y
results     <- sort(results)
plot(1:length(results), results, col = (as.numeric(names(results)) + 1), pch = 20,
     xlab = "Sorted Example", ylab = "Response")
```